### 2016-10-13 README.Rmd
add appveyor #175

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)

>>>>

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![codecov.io](https://codecov.io/github/ropensci/EML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/EML?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ropensci/EML?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/EML)
